---
title: 'R Programming: Homework 2'
author: "Hieu Pham"
output:
  pdf_document: default
  html_document: default
---

### **Instructions**
You can submit your homework in one of two ways.<br />

1. You can  fill in the missing code blocks directly in this .Rmd file (be sure to change the file name)<br />
2. You can create a new .R file and clearly label you answers. <br />

### **Getting Started**
In this assignment, we will be working with a stroke dataset which provides details about people who had strokes. Most columns are self-explanatory, but for more data details visit this website: https://www.kaggle.com/datasets/fedesoriano/stroke-prediction-dataset 

The packages listed below are simply suggestions, but please edit this list as you see fit.
```{r initiatePackages, message=FALSE, warning=FALSE}
## you can add more, or change...these are suggestions
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

### **Problem Set**

**1.**	Read in the `strokedata.csv` dataset, and remove any rows with missing values.

```{r}

```

**2.** Create two histograms using `ggplot2()`.

a. Showing the distribution of strokes<br />
b. Showing the distribution of age<br />

```{r}

```

**3.** Split your stroke.df dataframe into an 85/15 train/test split with a seed of 123.

```{r}



```


**4.**	Complete the following:

1. Create a logistic regression model on the response variable `stroke` using all columns as features
2. Print out a summary of your model
3. Which features are significant?


```{r}


```


**5.**	Using the logistic regression model complete the following:

1. Predict on your testing data frame
2. Compute your testing accuracy

```{r}


```
